PRIMUS: Effect of Galaxy Environment on the Quiescent Fraction Evolution at \lowercase{\textit{z}}$<0.8$

### 2015-03-18 qfenv_paper/ApJ submission/qf_environment.tex
address referee report
responses to minor comments on ref report

We now have a stellar mass complete sample derived from SDSS-{\em
  GALEX} and PRIMUS data. Since our sample is derived from two
different surveys, we account for the disparity in the redshift
uncertainty. While PRIMUS provides a large number of redshifts out to
$z = 1$, due to its use of a low dispersion prism, the redshift
uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5
\%$) than the uncertainties of the SDSS-{\em GALEX} redshifts. In order to have
comparable environment measures throughout our redshift range, we
apply PRIMUS redshift uncertainties to our galaxy sample selected from
SDSS-{\em GALEX}. For each SDSS-{\em GALEX} galaxy, we adjust its
redshift by randomly sampling a Gaussian distribution with standard
deviation $\sigma = 0.005 (1+z_{\mathrm{SDSS}-GALEX})$, where
$z_{\mathrm{SDSS}-GALEX}$ is the redshift of the galaxy.

@@

For our aperture, we use a cylinder of dimensions: $R_{\mathrm{ap}} =
\apradius\;
\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$.  We use a
cylindrical aperture to account for the PRIMUS redshift
errors and redshift space distortions (i.e. ``Finger of God"
effect). As \cite{Cooper:2005aa} and \cite{Gallazzi:2009aa} find, 
$\pm 1000 \; \mathrm{km} \;\mathrm{s^{-1}}$ optimally reduces the effects of redshift space
distortions. The PRIMUS redshift uncertainty at $z \sim 0.7$
corresponds to $\sigma_z < 0.01$, so our choice of $\apheight\;
\mathrm{Mpc}$ for the aperture height accounts for both of these effects. Our choice of
cylinder radius was motivated by scale dependence analyses in the
literature (\citealt{Blanton:2006aa, Wilman:2010aa, Muldrew:2012aa}),
which suggest that galactic properties such as color and quiescent
fractions are most strongly dependent on scales $< 2$ Mpc, around the
host dark matter halo sizes.

@@

Although we imposed PRIMUS redshift errors on our SDSS galaxies to consistently measure environment throughout our entire sample, we note a significant discrepancy between the $n_{\mathrm{env}}$ distributions of the SDSS and PRIMUS samples. For example, in each of the PRIMUS redshift bins, $\sim 40 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $\sim 20 \%$ of galaxies in the redshift bin are in low density environments and $\sim 35 \%$ are in high density environments. We remind the reader that this is mainly due to the varying stellar mass-completeness limits imposed on our galaxy sample for each redshift bins and does not affect our results. 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig3.pdf, height=0.75\textwidth,angle=90}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
low (left) and high (right) density environments throughout the redshift range
$z=0$--$0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=\apradius \: \mathrm{Mpc}$ and $H=\apheight \: \mathrm{Mpc}$ and  
classified as low environment when $n_{\mathrm{env}} < 0.5$ and as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
width $\Delta \mathrm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}      \label{fig:smf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results: Stellar Mass Function} \label{sec:smf}
Our galaxy sample has so far been classified into quiescent or
star-forming and low or high density environments. We further divide
these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$,
$0.4-0.6$, and $0.6-0.8$ for a total of 16 subsamples. In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples. Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION CALCULATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
To calculate the SMFs we employ a non-parametric $1/{V_{\mathrm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions in order to account for Malmquist bias, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\mathrm{log}\: \mathcal{M}) \Delta(\mathrm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\mathrm{max,avail},i}}. 
\end{equation}
$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\mathrm{log}\:
\mathcal{M}) \Delta(\mathrm{log}\: \mathcal{M})$ is the number of galaxies
($N$) per unit volume within the stellar mass range $[\mathrm{log}
  \mathcal{M},\: \mathrm{log} \mathcal{M}+\Delta(\mathrm{log}\mathcal{M})]$. The equation above is the same as Equation 3 in \cite{Moustakas:2013aa} except that we use $V_{\mathrm{max,avail}}$ instead than $V_{\mathrm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.

@@

For our PRIMUS sample at $z \sim 0.3$, over $10^{9.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11} \mathcal{M}_{\odot}$ $f_{\mathrm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.65$ for low density environment, while at high density environment $f_{\mathrm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.8$. Similarly, at $z \sim 0.5$, over $10^{10} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.2} \mathcal{M}_{\odot}$ $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.6$ for low density environment and $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.7$. Finally in our highest redshift bin $z \sim 0.7$, over the mass range $10^{10.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$, $f_{\mathrm{Q}}$ ranges from $\sim 0.35$ to $\sim 0.6$ for low density and $\sim 0.45$ to $\sim 0.8$ for high density. For the entire redshift range of our sample, $f_{\mathrm{Q}}$ in high density environment is higher than $f_{\mathrm{Q}}$ in low density environments.

@@

From our analyses we find the following notable results. The first
three demonstrate that previous findings that are well known in the
local universe are applicable out to $z\sim 0.7$. The last two are
consistent with the findings of \cite{Peng:2010aa} but provide increased
detail on the environmental dependence of galaxy evolution:
\begin{enumerate}
	\item From the SMFs, we find that the galaxy population in high
    density environments, both star-forming and quiescent, have a
    higher median mass, thus confirming the mass-density relation and
    mass-segregation in different environments throughout our sample's
    redshift range.
	\item For all subsamples, $f_{\mathrm{Q}}$ increases monotonically with
    galaxy stellar mass, showing a clear mass dependence and
    reflecting the well-established color-mass and morphology-mass
    relations.
	\item We illustrate that $f_{\mathrm{Q}}$ in high density environments
    is greater than $f_{\mathrm{Q}}$ in low density environments
    regardless of mass and out to redshift $z\sim 0.7$. This result
    reflects the well known trend that galaxies in high density
    environment are statistically redder, have lower SFRs, and are
    more massive.
	\item $f_{\mathrm{Q}}$ increases significantly with redshift for both
    low and high density environments. For high density environment,
    this trend is the Butcher-Oemler effect. Furthermore, the
    $f_{\mathrm{Q}}$ evolution in low density environment suggest the
    existence of internal environment-independent mechanisms for
    ending star formation.
	\item Comparison of the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$
    evolution for a range of environment classifications reveals that
    the since $z = 0.8$, $f_{\mathrm{Q}}$ has evolved by a greater amount
    in the highest density environments. For our purest high
    environment sample ($n_{\mathrm{env}} > 7$), the total $f_{\mathrm{Q}}$
    evolution is $\sim 0.1$ greater than the total $f_{\mathrm{Q}}$
    evolution in low density environment, revealing a moderate
    dependence on environment.
\end{enumerate}

>>>>

We now have a stellar mass complete sample derived from SDSS-{\em
  GALEX} and PRIMUS data. Since our sample is derived from two
different surveys, we account for the disparity in the redshift
uncertainty. While PRIMUS provides a large number of redshifts out to
$z = 1$, due to its use of a low dispersion prism, the redshift
uncertainties are significantly larger ($\sigma_{z}/(1+z) \approx 0.5
\%$) than the uncertainties of the SDSS redshifts. In order to have
comparable environment measures throughout our redshift range, we
apply PRIMUS redshift uncertainties to our galaxy sample selected from
SDSS-{\em GALEX}. For each SDSS-{\em GALEX} galaxy, we adjust its
redshift by randomly sampling a Gaussian distribution with standard
deviation $\sigma = 0.005 (1+z_\mathrm{SDSS})$, where
$z_\mathrm{SDSS}$ is the SDSS redshift of the galaxy.

@@

For our aperture, we use a cylinder of dimensions: $R_{\mathrm{ap}} = \apradius\;
\mathrm{Mpc}$ and $H_{\mathrm{ap}} = \apheight\; \mathrm{Mpc}$. 
We note that $H_\mathrm{ap}$ is the full height of the cylinder and $R_\mathrm{ap}$ 
and $H_\mathrm{ap}$ are comoving distances. We use a
cylindrical aperture to account for the PRIMUS redshift
errors and redshift space distortions (i.e. ``Finger of God"
effect). As \cite{Cooper:2005aa} and \cite{Gallazzi:2009aa} find, 
$\pm 1000 \; \mathrm{km} \;\mathrm{s^{-1}}$ optimally reduces the effects of redshift space
distortions. The PRIMUS redshift uncertainty at $z \sim 0.7$
corresponds to $\sigma_z < 0.01$, so our choice of $\apheight\;
\mathrm{Mpc}$ for the aperture height accounts for both of these effects. Our choice of
cylinder radius was motivated by scale dependence analyses in the
literature (\citealt{Blanton:2006aa, Wilman:2010aa, Muldrew:2012aa}),
which suggest that galactic properties such as color and quiescent
fractions are most strongly dependent on scales $< 2$ Mpc, around the
host dark matter halo sizes.

@@

Although we imposed PRIMUS redshift errors on our SDSS galaxies to consistently measure environment throughout our entire sample, we note a significant discrepancy between the $n_{\mathrm{env}}$ distributions of the SDSS and PRIMUS samples. For example, in each of the PRIMUS redshift bins, $\sim 40 \%$ of galaxies in the redshift bin are in low density environments and roughly $30 \%$ are in high density environments. In contrast, in the SDSS redshift bin, $\sim 20 \%$ of galaxies in the redshift bin are in low density environments and $\sim 35 \%$ are in high density environments. We remind the reader that this is mainly due to the varying stellar mass-completeness limits imposed on our galaxy sample for each redshift bins and does not affect our results. 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig3.pdf, height=0.75\textwidth}
     \caption{Evolution of stellar mass functions of star-forming (top) and quiescent (bottom) galaxies in 
low (left) and high (right) density environments throughout the redshift range
$z=0$--$0.8$. The environment of each galaxy  
was calculated using a cylindrical aperture size of $R=\apradius \: \mathrm{Mpc}$ and $H=\apheight \: \mathrm{Mpc}$ and  
classified as low environment when $n_{\mathrm{env}} < 0.5$ and as high environment when $n_{\mathrm{env}} > 3.0$. The SMFs use mass bins of 
width $\Delta \mathrm{log}(\mathcal{M}/\mathcal{M}_{\odot})=0.2$. In each panel we use shades of blue 
(star-forming) and orange (quiescent) to represent the SMF at different redshift, higher redshifts being
progressively lighter.}      \label{fig:smf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results: Stellar Mass Function} \label{sec:smf}
Our galaxy sample has so far been classified into quiescent or
star-forming and low or high density environments. We further divide
these subsamples into redshift bins: $0.05-0.12$, $0.2-0.4$,
$0.4-0.6$, and $0.6-0.8$ for a total of 16 subsamples. In Section \ref{sec:smfcalc}, we calculate the SMF for each of these subsamples. Then we examine the evolution of active and quiescent subsample SMFs in different environments in Section \ref{sec:smfevol}.  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% STELLAR MASS FUNCTION CALCULATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Stellar Mass Function Calculations} \label{sec:smfcalc} 
To calculate the SMFs we employ a non-parametric $1/{V_{\mathrm{max}}}$ estimator commonly used for galaxy luminosity functions and stellar mass functions in order to account for Malmquist bias, as done in \cite{Moustakas:2013aa} and discussed in the review \cite{Johnston:2011aa}. The differential SMF is given by the following equation:
\begin{equation} \label{eq:phi}
\Phi(\mathrm{log}\: \mathcal{M}) \Delta(\mathrm{log} \:\mathcal{M}) = \sum\limits_{i=1}^{N} \frac{w_i}{V_{\mathrm{max,avail},i}}. 
\end{equation}
$w_i$ is the statistical weight of galaxy $i$ and $\Phi(\mathrm{log}\:
\mathcal{M}) \Delta(\mathrm{log}\: \mathcal{M})$ is the number of galaxies
($N$) per unit volume within the stellar mass range $[\mathrm{log}
  \mathcal{M},\: \mathrm{log} \mathcal{M}+\Delta(\mathrm{log}\mathcal{M})]$. The equation above is the same as Equation 3 in \cite{Moustakas:2013aa} except that we use $V_{\mathrm{max,avail}}$ instead than $V_{\mathrm{max}}$, to account for the edge effects of the survey discussed in Section \ref{sec:edgeeffect}.

@@

For our PRIMUS sample at $z \sim 0.3$, over $10^{9.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11} \mathcal{M}_{\odot}$ $f_{\mathrm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.65$ for low density environment, while at high density environment $f_{\mathrm{Q}}$ ranges from $\sim 0.2$ to $\sim 0.8$. Similarly, at $z \sim 0.5$, over $10^{10} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.2} \mathcal{M}_{\odot}$ $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.6$ for low density environment and $f_{\mathrm{Q}}$ ranges from $\sim 0.3$ to $\sim 0.7$ for high density environments. Finally in our highest redshift bin $z \sim 0.7$, over the mass range $10^{10.5} \mathcal{M}_{\odot} < \mathcal{M}_{*} < 10^{11.5} \mathcal{M}_{\odot}$, $f_{\mathrm{Q}}$ ranges from $\sim 0.35$ to $\sim 0.6$ for low density and $\sim 0.45$ to $\sim 0.8$ for high density. For the entire redshift range of our sample, $f_{\mathrm{Q}}$ in high density environment is higher than $f_{\mathrm{Q}}$ in low density environments.

@@

From our analyses we find the following notable results. The first
three demonstrate that previous findings that are well known in the
local universe are applicable out to $z\sim 0.7$. The last two are
consistent with the findings of \cite{Peng:2010aa} but provide increased
detail on the environmental dependence of galaxy evolution:
\begin{enumerate}
	\item From the SMFs, we find that the galaxy population in high
    density environments, both star-forming and quiescent, have a
    higher median mass, thus confirming the mass-density relation and
    mass-segregation in different environments throughout our sample's
    redshift range.
	\item For all subsamples, $f_{\mathrm{Q}}$ increases monotonically with
    galaxy stellar mass, showing a clear mass dependence and
    reflecting the well-established color-mass and morphology-mass
    relations.
	\item We illustrate that $f_{\mathrm{Q}}$ in high density environments
    is greater than $f_{\mathrm{Q}}$ in low density environments
    for $\mathcal{M} \sim 10^{10.5} -10^{11} \mathcal{M}_\odot$ and out to redshift $z\sim 0.7$. This result
    reflects the well known trend that galaxies in high density
    environment are statistically redder, have lower SFRs, and are
    more massive.
	\item $f_{\mathrm{Q}}$ increases significantly with redshift for both
    low and high density environments. For high density environment,
    this trend is the Butcher-Oemler effect. Furthermore, the
    $f_{\mathrm{Q}}$ evolution in low density environment suggest the
    existence of internal environment-independent mechanisms for
    ending star formation.
	\item Comparison of the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$
    evolution for a range of environment classifications reveals that
    the since $z = 0.8$, $f_{\mathrm{Q}}$ has evolved by a greater amount
    in the highest density environments. For our purest high
    environment sample ($n_{\mathrm{env}} > 7$), the total $f_{\mathrm{Q}}$
    evolution is $\sim 0.1$ greater than the total $f_{\mathrm{Q}}$
    evolution in low density environment, revealing a moderate
    dependence on environment.
\end{enumerate}
